---
title: "shinyapp_iris_presentation"
author: "Powell Chu"
date: "1/25/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Iris dataset

A summary of the dataset *Iris* is as follows:
```{r iris, echo=F, message=F, warning=F}
## Iris dataset
data("iris")
library(ggplot2)
library(tidyr)
library(dplyr)
library(cluster)
library(factoextra)
library(ggplot2)
summary(iris)
```

## Histogram

Here we illustrate the histogram of the iris dataset on its variable (Sepal Length), separating by Species

```{r hist, echo=F, message=F, warning=F}
ind <- 1
ggplot(iris[, c(ind,5)], 
       aes(x=Sepal.Length, fill=Species)) +
    geom_histogram(stat = "bin", bins = 30) +
    xlab('# of bins')
```

## Linear Model

I also created a linear model with shiny app with the ability to change the predictor and outcome variables.

```{r lm1, warning = F, message = F, echo=F}
data <- iris[, c(1,2,5)]
colnames(data) <- c("x","y","c")
model1 <- lm(y ~ x, data=data)

p <- data %>% ggplot(aes(x = x, 
                            y = y,
                            col = c)) + 
    geom_point() +
    theme(legend.title = element_blank())

model2lines <- predict(model1, newdata = data.frame(x = 0:10))
output_df <- data.frame(x = 0:10,
                        y = model2lines,
                        c = 'linear model')
p <- p + geom_line(data = output_df, aes(x = x, y = y, col = c))
p
```


## K-means Clustering

Lastly, I examined the k-means clustering model with shiny app, with the ability to let user to select the number of clusters.

```{r cluster, warning = F, message = F, echo=F}
data <- iris[,c(1,2)]
set.seed(123)
model3 <- kmeans(data, 3, nstart = 25)
fviz_cluster(model3, geom = "point", data = data)
```

